An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-03-09 tex/paper.tex
Adding references for other python packages.

\begin{itemize}
    \item Machine learning (\url{http://scikit-learn.org/});
    \item Visualisation (\url{http://matplotlib.org/});
    \item Mathematics (\url{http://www.sagemath.org/});
    \item Astrophysics (\url{http://www.astropy.org/});
    \item Data manipulation (\url{http://pandas.pydata.org/});
    \item Algorithmic Game Theory (\url{http://gambit.sourceforge.net/)}).
\end{itemize}

>>>>

\begin{itemize}
    \item Machine learning \cite{scikit-learn} (\url{http://scikit-learn.org/});
    \item Visualisation \cite{Hunter:2007} (\url{http://matplotlib.org/});
    \item Mathematics \cite{sage} (\url{http://www.sagemath.org/});
    \item Astrophysics \cite{astropy} (\url{http://www.astropy.org/});
    \item Data manipulation \cite{mckinney-proc-scipy-2010} (\url{http://pandas.pydata.org/});
    \item Algorithmic Game Theory \cite{Mckelvey06gambit:software} (\url{http://gambit.sourceforge.net/})).
\end{itemize}
